---
title: Marketing Data Analysis
author: Berk Yılmaz
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE)
```

```{r}
#Importing the dataset and loading necessary packages
library(readr)
library(dplyr)
library(lmtest)
library(ggplot2)
library(tidyr)
library(patchwork)
library(corrplot)

Survey_Data <- read_csv("Survey_Results.csv")

Survey_Data
```

# Removing Redundant Columns


```{r}
Survey_Data <- Survey_Data %>% select(-"StartDate", -"EndDate", -"Status", -"IPAddress", -"Progress", -"Duration (in seconds)", -"Finished", -"RecordedDate", -"ResponseId", -"RecipientLastName", -"RecipientEmail", -"ExternalReference", -"LocationLatitude", -"LocationLongitude", -"DistributionChannel", -"UserLanguage", -"Q_RecaptchaScore", -"QID34", -"RecipientFirstName")
  
Survey_Data <- Survey_Data[-c(1, 2), ]

```

# Removing every column with the word "TEXT" in them because we cannot perform statistical analysis on sentences.

```{r}
Survey_Data <- Survey_Data %>% select(-contains("TEXT"))

#Turn every column except Question 8 and 16 into numeric
Survey_Data <- Survey_Data %>%
  mutate(across(.cols = -c(Q8, Q16), .fns = ~ as.numeric(as.character(.))))

#Giving logical names to each question's column for ease of interpretation
Survey_Data <- Survey_Data %>%
  rename(
    Age = Q1,
    Gender = Q2,
    Place_of_birth = Q3,
    Reg_Coca = Q4,
    Reg_SoftBev = Q5,
    Why_SoftBev = Q6, 
    Why_No_SoftBev = Q7, 
    Which_Softdrink_reg = Q8,
    Try_New_Softdrink = Q9,
    Sit_New_Softdrink = Q10,
    Color_importance = Q11,
    Colorful_or_Dark = Q12,
    Packaging = Q13,
    Origin_importance = Q14,
    Foreign_bev = Q15,
    Foreign_bev_why = Q16,
    History_domestic = Q17,
    Fernandes_familiar = Q18, 
    Fernandes_origin = Q19,
    Fernandes_continent = Q20,
    Fernandes_customer = Q21,
    Fernandes_motivation = Q22,
    Fernandes_flavour = Q23
  )

```

# Now, we will take the crucial step of reversing the order of numbers for a certain column by mapping each value to its new counterpart in the reversed order. The reason why we do this is to uniformize the data where features that positively impact Fernandes consumption will take on larger positive numbers and vice versa. This will make the interpretation of the coefficients in the sample regression much simpler.

```{r}
# Define the reverse function
reverse_values <- function(column, max_value) {
  column <- as.numeric(as.character(column))
  return(max_value + 1 - column)
}

# Apply the reversal function to the Q4, Q5 columns and replacing the original column
Survey_Data$Reg_Coca <- reverse_values(Survey_Data$Reg_Coca, 4)
Survey_Data$Reg_SoftBev <- reverse_values(Survey_Data$Reg_SoftBev, 4)
Survey_Data$Fernandes_familiar <- reverse_values(Survey_Data$Fernandes_familiar, 3)
Survey_Data$Fernandes_origin <- reverse_values(Survey_Data$Fernandes_origin, 4)
Survey_Data$Fernandes_customer <- reverse_values(Survey_Data$Fernandes_customer, 3)

# A display of the updated Survey_Data
Survey_Data

```

# Running the Regression

```{r}

model <- lm(Fernandes_customer ~ Age + Gender + Place_of_birth + Reg_Coca + Reg_SoftBev + Try_New_Softdrink + Sit_New_Softdrink + Color_importance + Colorful_or_Dark + Packaging + Origin_importance + Fernandes_origin + Fernandes_motivation + Fernandes_flavour + Fernandes_familiar + Fernandes_continent, data = Survey_Data)

summary(model)

```

# Testing for Heteroskedasticity

```{r}
bptest(model)
```

Heteroskedasticity is not present. So no need for robust standard errors.


# Visualizing the Relationship


```{r}
#The relationship etween Fernandes brand Familiarity and Consumption across different age groups
Survey_Data %>% group_by(Age) %>% summarise(mean_familiarity = mean(Fernandes_familiar), mean_consumption = mean(Fernandes_customer))

```

# Bar Chart of Fernandes Brand Familarity and Consumption across Age Groups

```{r}
# Calculating mean familiarity and consumption by age
age_group_summary <- Survey_Data %>%
  group_by(Age) %>%
  summarise(mean_familiarity = mean(Fernandes_familiar, na.rm = TRUE),
            mean_consumption = mean(Fernandes_customer, na.rm = TRUE))

# Creating the data frame that we will use for this graph
age_group_long <- age_group_summary %>%
  pivot_longer(cols = c(mean_familiarity, mean_consumption), names_to = "Variable", values_to = "Value")

# Personally choosing the color palette
colors <- c("mean_familiarity" = "#6BAED6", "mean_consumption" = "#FB6A4A")

# The Bar Chart
ggplot(age_group_long, aes(x = factor(Age), y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  labs(title = "Fernandes Brand Familiarity and Consumption Across Age Groups",
       x = "Age Group",
       y = "Mean Value",
       fill = "Metric") +
  theme(axis.text.x = element_text(hjust = 1),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.title = element_text(face = "bold"),
        legend.position = "bottom")
```

# Sample Regression for Those Who Correctly Identified the Continent of Suriname

```{r}
# Filtering the data for respondents who correctly identified the location
correct_respondents <- Survey_Data %>% filter(Fernandes_continent == 4)

# Sample Regression
model_correct <- lm(Fernandes_customer ~ Age + Gender + Place_of_birth + Reg_Coca + Reg_SoftBev + Try_New_Softdrink + Sit_New_Softdrink + Color_importance + Colorful_or_Dark + Packaging + Origin_importance + Fernandes_origin + Fernandes_motivation + Fernandes_flavour + Fernandes_familiar + Fernandes_origin, data = correct_respondents)

# Summary
summary(model_correct)

```

The coefficient for Fernandes_familiar is even more negative than in the regression for every respondant, which indicates that for individuals who correctly identified Suriname's location, there's an even more negative chance of them being a Fernandes customer if they are familiar with the brand. This may be caused by possible prejudice.

# Bar chart of Fernandes Familiarity and Consumption across age groups for those who correctly identified Suriname

```{r}
correct_respondents <- Survey_Data %>% filter(Fernandes_continent == 4)

age_group_summary_correct <- correct_respondents %>%
  group_by(Age) %>%
  summarise(mean_familiarity = mean(Fernandes_familiar, na.rm = TRUE),
            mean_consumption = mean(Fernandes_customer, na.rm = TRUE))

age_group_long_correct <- age_group_summary_correct %>%
  pivot_longer(cols = c(mean_familiarity, mean_consumption), names_to = "Variable", values_to = "Value")

colors <- c("mean_familiarity" = "#6BAED6", "mean_consumption" = "#FB6A4A")

ggplot(age_group_long_correct, aes(x = factor(Age), y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  labs(title = "Fernandes Brand Familiarity and Consumption Across Age Groups (Correct Respondents)",
       x = "Age Group",
       y = "Mean Value",
       fill = "Metric") +
  theme(axis.text.x = element_text(hjust = 1),
        plot.title = element_text(hjust = 0.3, face = "bold"),
        legend.title = element_text(face = "bold"),
        legend.position = "bottom")

```

# Visualization of being a Fernandes Customer across Different Continents of Birth

```{r}
# Calculate mean consumption by origin category
mean_consumption_by_origin <- Survey_Data %>%
  group_by(Place_of_birth) %>%
  summarise(mean_consumption = mean(Fernandes_customer, na.rm = TRUE))

# Plot the bar chart
ggplot(mean_consumption_by_origin, aes(x = Place_of_birth, y = mean_consumption, fill = Place_of_birth)) +
  geom_bar(stat = "identity", color = "black") +
  theme_minimal() +
  labs(title = "Mean of Fernandes Consumption by Origin",
       x = "Place of Birth",
       y = "Mean Consumption") +
  theme(axis.text.x = element_text(hjust = 1),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")
```
Where 1 stands for Asia, 2 for Africa, 3 for North America, 4 for South America and 6 for Europe.


# The Correlation Matrix 

```{r}
# Ensuring we only calculate correlations for numeric columns
numeric_columns <- Survey_Data %>% select(where(is.numeric))
cor_matrix <- cor(numeric_columns, use = "complete.obs")

# The Corr Matrix
corrplot(cor_matrix, method = "circle", type = "upper", tl.col = "black", tl.cex = 0.8)


```

